Self Regulation Ontology Retest Data Report

### 2017-04-13 SRO_Report.Rmd
added average reliabilities per task

Summarize all raw per task

```{r warning=FALSE, message=FALSE}
measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -measure_type, -task) %>%
  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
  gather(key, value, -dv, -icc, -spearman, -num_all_trials) %>%
  arrange(dv) %>%
  drop_na() %>%
  mutate(value = trim(value))
```

Does number of items in a trial have a significant effect on the average reliability of raw measures from a task?

```{r}
summary(lm(icc ~ num_all_trials))
```

>>>>

We filter out the DDM parameters and measures for specific contrasts. Note that this does leave some tasks with measures that are model fits and/or for specific conditions (because at least the current datasets do not include measures that are based on all the trials **and** are raw though I could dive in to variables_exhaustive for such measures). Here's the order of tasks by mean reliability sorted for ICC and then Spearman's $\rho$.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -measure_type, -task) %>%
  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
  separate(variable_type, c("label_1", "label_2", "label_3"), sep = ",") %>%
  mutate(label_1 = trim(label_1),
         label_2=trim(label_2),
         label_3=trim(label_3))%>%
  filter(label_1 %in% c('difference', 'EZ', 'hddm') ==FALSE & label_2 %in% c('difference', 'EZ', 'hddm') == FALSE) %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(mean_icc = mean(icc),
            mean_spearman = mean(spearman),
            num_measures = n(),
            num_trials = unique(num_all_trials)) %>%
  arrange(-mean_icc, -mean_spearman)

tmp
```

Does number of items in a task have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.

```{r warning=FALSE, message=FALSE}
summary(lm(mean_icc ~ num_trials, data = tmp))
```

Does number of items in a task have a significant effect on the average Spearman $\rho$ of (mostly) raw measures for all trials from a task? No.

```{r warning=FALSE, message=FALSE}
summary(lm(mean_spearman ~ num_trials, data = tmp))
```

Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task? No.

```{r warning=FALSE, message=FALSE}
summary(lm(mean_icc ~ num_measures, data = tmp))
```

Does number of measures that went in to this reliability estimate have a significant effect on the average ICC of (mostly) raw measures for all trials from a task?  
The regression suggests that the more measures that went in to the averaging of Spearman's $\rho$'s the lower the mean Spearman $\rho$ for that task. This might suggest that this way of summarizing data might not be a good idea in general or at least that we shouldn't do it for the Spearman correlations.

```{r warning=FALSE, message=FALSE}
summary(lm(mean_spearman ~ num_measures, data = tmp))
```
